% acknowledgments.tex
% 
% LaTeX document from NYU music technology master's thesis


\begin{acknowledgements}

\par \vskip \baselineskip
\noindent
This thesis is based on research conducted in the Fall of 2015 at \'Ecole normale sup\'erieure in Paris. As a visiting researcher in the Data Processing and Classification team, I was able to work closely with those primarily responsible for the scattering transform's many successes over its as-yet short lifespan, and contributing in any small way to this bevy of research has been a humbling and deeply gratifying experience. My many thanks to St\'ephane Mallat, who so graciously invited me to his team and supported me throughout my stay. I owe much of the work in this thesis to my teammates Vincent Lostanlen and Carmine Emanuele Cella, who have guided and advised me at numerous points throughout this work. I would also like to thank Sira, Ir\`ene, Mathieu, Amos, and everyone else who so warmly welcomed me to ENS and made my stay so enjoyable and productive.

\par \vskip \baselineskip
\noindent
I would like to thank Juan Bello for initiating this research project, making the link with the team at ENS, and advising me throughout the initial research and multiple paper write-ups. He has been an excellent advisor, always forcing me to think deeper at each stage and discover the fundamental aspects at play in such increasingly complex problems. I would like to also thank all in the MIR team at NYU, primarily Taemin Cho for providing the state-of-the-art research in the first place, and Rachel Bittner, Eric Humphrey, and Brian McFee for their help along the way.

\par \vskip \baselineskip
\noindent
Agnieszka Roginska has provided endless support and guidance throughout the past two and a half years, and I am deeply grateful to her for it. It has been a pleasure being her research assistant, and I would like to thank Andrea Genovese, Areti Andreopoulou, and everyone else who has contributed to the Immersive Audio's team research. Thanks as well to all of the faculty at Steinhardt's Music Technology program and the Courant Institute who have impacted my studies. 

\par \vskip \baselineskip
\noindent
Jordan Juras and Dave Tatasciore have proven invaluable sounding boards over these past years, putting up with many rants over even more beers.

\par \vskip \baselineskip
\noindent
Most importantly I would like to thank my partner Iliana for everything. Very little of this work would have been possible without her unwavering support.

\end{acknowledgements}